






lod_filtr_dx11 -2.5
lod_filtr_dx9 -0.5
texture_lod 2

r1_software_skinning 0


r2_allow_r1_lights off
r2_ao on
r2_ao_quality st_opt_low
r2_bloom_type st_opt_csky
r2_detail_bump off


r2_dof_enable on
r2_dof_kernel 2.
r2_dof_weather on

r2_exp_donttest_shad off
r2_gasmask 0.
r2_gasmask_effect 1
r2_gloss_build_2218 off
r2_gloss_factor 1.
r2_ls_bloom_fast off
r2_ls_bloom_kernel_b 0.7
r2_ls_bloom_kernel_g 3.
r2_ls_bloom_kernel_scale 0.7
r2_ls_bloom_speed 100.
r2_ls_bloom_threshold 1.
r2_ls_depth_bias -0.0003
r2_ls_depth_scale 1.00001
r2_ls_dsm_kernel 0.7
r2_ls_psm_kernel 0.7
r2_ls_squality 0.7
r2_ls_ssm_kernel 0.7
r2_mblur 0.2
r2_mblur_enable off
r2_parallax_h 0.02
r2_particle_distance 331.40002
r2_rain_drops 1
r2_rain_drops_diff 0
r2_slight_fade 0.5
r2_smap_size SM_2
r2_soft_particles on
r2_soft_water on


r2_ssa_lod_a 96.
r2_ssa_lod_b 64.
r2_steep_parallax off
r2_steep_parallax_distance 100.
r2_steep_parallax_h 0.013
r2_steep_parallax_samples 100.
r2_steep_parallax_samples_min 5.
r2_sun on
r2_sun_depth_far_bias -0.00002
r2_sun_depth_far_scale 1.
r2_sun_depth_near_bias 0.00001
r2_sun_depth_near_scale 1.
r2_sun_details off
r2_sun_far 100.
r2_sun_flares on
r2_sun_focus on
r2_sun_lumscale 1.35
r2_sun_near 20.
r2_sun_near_border 0.75
r2_sun_quality st_opt_medium
r2_sun_shafts st_opt_medium
r2_sun_tsm on
r2_sun_tsm_bias -0.01
r2_sun_tsm_proj 0.3
r2_sunshafts_mode volumetric
r2_tonemap on
r2_tonemap_adaptation 1.
r2_tonemap_amount 0.7
r2_tonemap_lowlum 0.0001
r2_tonemap_middlegray 0.45
r2_vignette 0
r2_volum_distance 1.
r2_volum_intensity 0.1
r2_volum_quality 0.35
r2_volumetric_fog 1
r2_volumetric_lights off

r2_zfill off
r2_zfill_depth 0.25

r3_adv_wet_hud 1
r3_backbuffers_count 1
r3_dynamic_wet_surfaces on
r3_dynamic_wet_surfaces_far 50.5
r3_dynamic_wet_surfaces_near 23.5
r3_dynamic_wet_surfaces_opt 0
r3_dynamic_wet_surfaces_sm_res 640
r3_hud_rain_drops 0
r3_hud_visor_effect 0
r3_hud_visor_shadowing 0
r3_minmax_sm autodetect
r3_msaa st_opt_off
r3_msaa_alphatest st_opt_off
r3_rain_4p 0
r3_technicolor 0
r3_use_dx10_1 off
r3_vibrance 0.1
r3_volumetric_smoke on







r4_enable_tessellation off
r4_tess_quality st_tess_low
r4_wireframe off
r__actor_shadow off
r__clear_models_on_unload 0
r__detail_density 0.4
r__detail_radius 110
r__detail_scale 0.5
r__dtex_range 50.
r__dtexture_dist_f 1.
r__enable_grass_shadow 0
r__geom_discard_dist_f 1.7
r__geom_quality_dist_f 1.5
r__geometry_lod 1.8
r__lod_sprite_dist_f 2.
r__no_scale_on_fade 0
r__ntexture_dist_f 2.
r__ssa_glod_end 64.
r__ssa_glod_start 256.
r__supersample 1
r__tf_aniso 8
r__use_precompiled_shaders 0
r__wallmark_ttl 50.
r_fps_lock fps 60

render_gamma 1.
render_type_aa FXAA



rs_fullscreen on

rs_skeleton_update 32
rs_stats off

rs_vis_distance 0.6
